---
title: "Adidas_US_Sales_ETL"
author: "Ahmed Essam"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

#### Loading libraries
```{r}
library(tidyverse)
library(lubridate)
```

#### Loading the data and explore its structure
```{r}
ADS <- read.csv('Adidas_US_Sales_Datasets.csv', stringsAsFactors = F)
str(ADS)
```

#### Exploring the first 10 columns of the data
```{r}
head(ADS, 10)
```

#### Exploring the last 10 columns of the data
```{r}
tail(ADS, 10)
```

#### Exploring 50 random observations of the data
```{r}
slice_sample(ADS, n=50)
```

## Data transformation
```{r}
ADS$Invoice.Date <- mdy(ADS$Invoice.Date)
```

```{r}
ADS$Retailer <- as.factor(ADS$Retailer)
ADS$Retailer.ID <- as.factor(ADS$Retailer.ID)
ADS$Region <- as.factor(ADS$Region)
ADS$State <- as.factor(ADS$State)
ADS$City <- as.factor(ADS$City)
ADS$Product <- as.factor(ADS$Product)
ADS$Sales.Method <- as.factor(ADS$Sales.Method)
```

```{r}
ADS$Price.per.Unit <- gsub('[^[:alnum:]]','',(ADS$Price.per.Unit))
ADS$Price.per.Unit <- as.numeric(ADS$Price.per.Unit)
ADS$Price.per.Unit <- as.numeric(format(round(ADS$Price.per.Unit*0.01, 2), nsmall=2))
```

```{r}
ADS$Units.Sold <- gsub('[^[:alnum:]]','',(ADS$Units.Sold))
ADS$Units.Sold <- as.integer(ADS$Units.Sold)
ADS$Total.Sales <- gsub('[^[:alnum:]]','',(ADS$Total.Sales))
ADS$Total.Sales <- as.integer(ADS$Total.Sales)
ADS$Operating.Profit <- gsub('[^[:alnum:]]','',(ADS$Operating.Profit))
ADS$Operating.Profit <- as.integer(ADS$Operating.Profit)
ADS$Operating.Margin <- gsub('[^[:alnum:]]','',(ADS$Operating.Margin))
ADS$Operating.Margin <- as.numeric(ADS$Operating.Margin)*0.01
```

```{r}
ADS <- ADS %>%
rename(RetailerID = Retailer.ID, InvoiceDate = Invoice.Date, UnitPrice = Price.per.Unit, Quantity = Units.Sold, Revenue = Total.Sales, OP = Operating.Profit, OPM = Operating.Margin, Method = Sales.Method)
```

```{r}
ADS$Year <- as.factor(year(ADS$InvoiceDate))
ADS$Month <- month(ADS$InvoiceDate, label = T)
```

#### Exploring the summary descriptive statistics of the dataset after tranfomation process
```{r}
summary(ADS)
```

### Finding outliers, subsetting and cleaning the dataset
```{r}
ADS %>%  arrange(desc(Revenue)) %>% head(n=50)
```

```{r}
ADS_HR <- ADS %>% filter(Revenue>=400000) %>% filter(Revenue<=710000)
summary(ADS_HR)
```

```{r}
ggplot(ADS_HR, aes(Revenue))+geom_boxplot()
```

```{r}
ADS_MR <- ADS %>% filter(Revenue<400000) %>% filter(Revenue>=10000)
summary(ADS_MR)
```

```{r}
ggplot(ADS_MR, aes(Revenue))+geom_boxplot()
```

```{r}
ADS_LR <- ADS %>% filter(Revenue<10000) %>% filter(Revenue !=0)
summary(ADS_LR)
```

```{r}
ggplot(ADS_LR, aes(Revenue))+geom_boxplot()
```

#### Saving the ETL version of data subsets
```{r}
write_rds(ADS, 'Adidas_US_Sales_Datasets_ETL.rds', compress = 'gz')
write_rds(ADS_HR, 'Adidas_US_Sales_High_Revenue_ETL.rds', compress = 'gz')
write_rds(ADS_MR, 'Adidas_US_Sales_Midium_Revenue_ETL.rds', compress = 'gz')
write_rds(ADS_LR, 'Adidas_US_Sales_Low_Revenue_ETL.rds', compress = 'gz')
```

```{r}
write_csv(ADS, 'Adidas_US_Sales_Datasets_ETL.csv')
write_csv(ADS_HR, 'Adidas_US_Sales_High_Revenue_ETL.csv')
write_csv(ADS_MR, 'Adidas_US_Sales_Midium_Revenue_ETL.csv')
write_csv(ADS_LR, 'Adidas_US_Sales_Low_Revenue_ETL.csv')
```




